---
title: "Cabbages"
author: "Kaylie Brehm"
date: "Summer 2022"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  
$H_0$:There is no difference in the average vitamin C content between cultivation method c39 and c52.

$H_A$: There is a difference in the average vitamin C content between cultivation method c39 and c52.

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->
To explain the vitamin C content, numerical, based on cultivation method, categorical, I will do a numerical categorical analysis. I will also complete a T-Test for the vitamin C content of the two cultivation methods for comparison.

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
Box Plot
```{r}
plot(VitC~Cult,data=veggy)
```

The median in cultivation method 39 is about 50, while the median in cultivation method 52 is about 10 higher. The lower and upper quartile values in c39 are also lower than c52. This means that based on the data so far, the vitamin C content is, on average, lower in cultivation method 39. 

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
Numerical Chart
```{r}
favstats(VitC~Cult,data=veggy)
```

The median in c39 is 51, while the mean is 51.5. The median in c52 is 64.5, and the mean is 64.4. Since mean measures averages, and the two means are different, the vitamin C content is proven to have different averages. It seems that cultivation method 52 produces more vitamin C content. 

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
T-Test Results
```{r}
t.test(VitC~Cult,data=veggy)
```

Based on the t-test, we can infer that the t value is 6.3909. The t value is the ratio of difference between the means in both cultivation levels. Since the ratio is is less than -2, the means are proven to be very different. The p-value is 0.00000003405. The p value represents the possibility of getting a sample that proves the null hypothesis to be true. Since the possibility is so small, I reject the null hypothesis. Our degree of freedom is fairly high at 56.376, so this validates our experiment. The larger the sample and the stronger the data, the better. Which is what these three values demonstrate. 

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
The inferential results prove that the experiment is valid due to its high degree of freedom. The inferential results also prove a large difference between the values of vitamin C content in different cultivation methods. Whether that difference is impacted from method, is up to debate. There could be an outlying cause. But it is for certain that the values are different. In conclusion, I reject the null hypothesis.

